A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments

### 2014-09-09 src/paper.tex
WIP: Experiment

The following URIs and HTTP methods describe some of the HTTP requests for viewers resources that were developed in this experiment:

\begin{itemize}
	\item \emph{/viewers} - POST: create a new viewer, as identified by the resource that is present in the URI. The parameters that are carried in this type of request are \emph{viewerId}, \emph{username}, and \emph{password}.
	\item \emph{/viewers/\{viewerId\}} - GET: retrieves a specific viewer identified by \{viewerId\} in the URI. This request retrieves information about the viewer, which in this case are only \emph{viewerId} and \emph{username}, since is not safe to include a \emph{password} in the response body.
	\item \emph{/viewers/\{viewerId\}/evaluations} - GET: Retrieve a collection of evaluations that were performed by a viewer identified by \{viewerId\}. Each evaluation contains a \emph{programId}, \emph{viewerId}, and a \emph{rating}.
\end{itemize}

@@

>>>>

The web services API consists in handling three types of resources: viewers, TV programs and programs evaluations. The following URIs and HTTP methods describe some of the HTTP requests for viewers resources that were developed in this experiment:

\begin{itemize}
	\item \emph{/viewers} - POST: creates a new viewer, as identified by the resource that is present in the URI. The parameters that are carried in this type of request are \emph{viewerId}, \emph{username}, and \emph{password}.
	\item \emph{/viewers/\{viewerId\}} - GET: retrieves a specific viewer identified by \{viewerId\} in the URI. This request retrieves information about the viewer, which in this case are only \emph{viewerId} and \emph{username}, since is not safe to include a \emph{password} in the response body.
	\item \emph{/viewers/\{viewerId\}/evaluations} - GET: retrieves a collection of evaluations that were performed by a viewer identified by \{viewerId\}. Each evaluation contains a \emph{programId}, \emph{viewerId}, and a \emph{rating}.
\end{itemize}

@@

\begin{itemize}
	\item \emph{/programs} - POST: creates a new TV program, so that it is available to be presented in the second screen clients. In this experiment, an on-line videos platform was used provide videos to second screen clients. 
	\item \emph{/programs} - GET: retrieves a collection of TV programs that are available on the CP. A TV program representation contains a \emph{programId}, a \emph{videoCode} (id of the video on the videos platform), and \emph{title} (a title for the video representing the program).
	\item \emph{/program/\{programId\}} - GET: retrieves a single program identified by \emph{programId}.
\end{itemize}

Resources related to the evaluations performed by viewers are handled by the following HTTP requests:
